### 2020-09-16 manuscript/paper_BRM.Rmd
add gamma distribution justification

On one hand, many of these classification algorithms use non-parametric methods to differentiate between eye movement events. For instance, the classic "Velocity-Threshold" algorithm classifies samples with a velocity above a fixed threshold as saccades [@Stample1993]. On the other hand, many parametric methods have been developed recently. Some of them require human labeled training data as input and can therefore be termed as supervised. For example, @Bellet2019 trained a convolutional neural network (CNN) on eye-tracking data from humans and macaques and achieved classification results that were similarly accurate to those of human coders. However, these supervised methods have several disadvantages: First, they require labeled data (usually labeled by humans) as input. Second, they often rely on hyperparameters which are difficult to theoretically justify. Third, their parameters are usually difficult to interpret: Most supervised methods operate in a black-box fashion, which implies that they don't make any explicit assumptions about the data generating process. Beyond that, there are several algorithms using unsupervised techniques. They typically don't need to be trained on labeled data and are also more flexible in classifying data from different individuals, tasks, or eye-trackers.  

@@

In the context of eye movements, HMMs are suitable models because the hidden states can be interpreted as eye movement events and gaze data are dependent time series (i.e., one gaze sample depends on the previous). Further, HMMs can be viewed as unsupervised models that can learn the hidden states and parameters of the emission process from the observed data alone, and as such do not in principle need training labeled data as it would be the case for supervised methods.  

@@

First, I-HMM relies on setting an appropriate threshold to determine the initial classification, which can distort the results [@Blignaut2009; @Komogortsev2010; @Shic2008]. Second, the current implementation of NSLR-HMM requires human-coded data, which narrows its applicability. It also inherits fixed parameters that prevent the algorithm to adapt to the individual- or task-specific signals. Third, BMD limits the classification to microsaccades which are irrelevant in many applications and sometimes even considered as noise [@Duchowski2017]. The opposite problem was observed for BP-AR-HMM: It tends to estimate an unreasonable number of events from the data of which many are considered as noise events. Therefore, the authors suggest using it as an exploratory tool followed by further event classification [@Houpt2018].  

@@

# The Algorithm
As illustrated in Figure \@ref(fig:plot-algorithm-workflow), most eye movement event classification algorithms consist of three steps: During *preprocessing*, the raw gaze position is transformed into a metric of position and/or time. Often, a filtering or smoothing procedure is applied to the data before or after the tranformation to separate the gaze signal from noise and artifacts [@Spakov2012]. It follows the *classification*, depending on the method and settings of the algorithm, each sample is labeled as a candidate for one of the predefined events. Lastly, as part of the *postprocessing*[^1], the algorithm decides which candidates to accept, relabel, or merge [@Hessels2017; @Komogortsev2010].

@@

It has to be noted that the gamma was chosen out of convenience and the best fitting distribution might be different between eye-trackers, subjects, and tasks.   

>>>>

On one hand, many of these classification algorithms use non-parametric methods to differentiate between eye movement events. For instance, the classic "Velocity-Threshold" algorithm classifies samples with a velocity above a fixed threshold as saccades [@Stample1993]. On the other hand, many parametric methods have been developed recently. Some of them require human labeled training data as input and can therefore be termed as supervised. For example, @Bellet2019 trained a convolutional neural network (CNN) on eye-tracking data from humans and macaques and achieved classification results that were similarly accurate to those of human coders. However, these supervised methods have several disadvantages: First, they require labeled data (usually labeled by humans) as input. Second, they often rely on hyperparameters which are difficult to theoretically justify. Third, their parameters are usually difficult to interpret: Most supervised methods operate in a black-box fashion, which implies that they do not make any explicit assumptions about the data generating process. Beyond that, there are several algorithms using unsupervised techniques. They typically do not need to be trained on labeled data and are also more flexible in classifying data from different individuals, tasks, or eye-trackers.  

@@

In the context of eye movements, HMMs are suitable models because the hidden states can be interpreted as eye movement events and gaze data are dependent time series (i.e., one gaze sample depends on the previous). Further, HMMs can be viewed as unsupervised models that can learn the hidden states and parameters of the emission process from the observed data alone, and as such do not in principle need labeled training data as it would be the case for supervised methods.  

@@

First, I-HMM relies on setting an appropriate threshold to determine the initial classification, which can distort the results [@Blignaut2009; @Komogortsev2010; @Shic2008]. Second, the current implementation of NSLR-HMM requires human-coded data, which narrows its applicability. It also inheres fixed parameters that prevent the algorithm to adapt to individual- or task-specific signals. Third, BMD limits the classification to microsaccades which are irrelevant in many applications and sometimes even considered as noise [@Duchowski2017]. The opposite problem was observed for BP-AR-HMM: It tends to estimate an unreasonable number of events from the data of which many are considered as noise events. Therefore, the authors suggest using it as an exploratory tool followed by further event classification [@Houpt2018].  

@@

# The Algorithm
As illustrated in Figure \@ref(fig:plot-algorithm-workflow), most eye movement event classification algorithms consist of three steps [cf. @Hessels2017]: During *preprocessing*, the raw gaze position is transformed into a metric of position and/or time. Often, a filtering or smoothing procedure is applied to the data, before or after the tranformation, to separate the gaze signal from noise and artifacts [@Spakov2012]. It follows the *classification*, depending on the method and settings of the algorithm, each sample is labeled as a candidate for one of the predefined events. Lastly, as part of the *postprocessing*[^1], the algorithm decides which candidates to accept, relabel, or merge [@Hessels2017; @Komogortsev2010].

@@

When we developed gazeHMM, the gamma distribution appeared to fit eye movement data well, but we also note that it might not necessarily be the best fitting distribution for every type of eye movement data. We assume that the best fitting distribution will depend on the task, eye-tracker, and individual (see also the discussion).  
